Modeling potential JCPOA diversion scenarios with Cyclus

### 2018-05-03 paper.tex
first draft of introduction

\documentclass{anstrans}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{Modeling potential JCPOA diversion scenarios with Cyclus}
\author{Baptiste Mouginot,$^{*}$ Kathryn Mummah,$^{*}$ Paul P.H. Wilson$^{*}$}

@@

\section{Cascade Enrich Construction}
\subsection{Centrifuge properties}

\subsection{Explored Cases}

>>>>

\documentclass{anstrans}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{}
\author{Baptiste Mouginot,$^{*}$ Kathryn Mummah,$^{*}$ Paul P.H. Wilson$^{*}$}

@@

Fuel cycle simulations, as any simulation process, do not produce results
without errors. Those errors have different sources: data uncertainties (when
the simulation relies on previously estimated/measured metrics), modeling
uncertainties (produced by the simplification made by the simulator) and the
``functional`` uncertainty (uncertainty on the operation parameters of the
different facilities).

Some treaty verification scenarios require estimating historical fissile
material production based on records of facility operation and material
transfer.  If the measurements of facility operation and material transfer are
subject to uncertainty, the total production quantities will then also be
uncertain, creating an opportunity for undetected diversion.  This study seeks
to understand which measures of facility operation have the most impact on the
uncertainty of fissile material production across a complete fuel cycle.  A
``Total Monte Carlo'' approach will be applied to the Cyclus fuel cycle simulator
\cite{cyclus} to estimate output metrics uncertainty caused by individual
facility uncertainties.

\section{Method}

To estimate the uncertainty on fuel cycle output metrics, a ``Total Monte
Carlo'' approach has been applied. In the following, output metric uncertainty
corresponds to the Standard Deviation of the output metrics over about 200
different simulations. For each uncertainty associated parameter, an
artificially large uncertainty of $10\%$ have been Normally distributed.

To pursuit this work, both the Cycamore\cite{cycamore} package and the
CyCLASS\cite{cyclass} have been updated to deal with uncertainty in different
operational parameters of their different facility.  Table
\ref{tab:package_uncertainty} summarize all the modification implemented in the
different facilities present in Cycamore and CyCLASS.

 \begin{table}[htb]
 \centering
   \caption{Summary of facility modification per source package.}
 \begin{tabular}{cll}
 \toprule

 Packae   & Facility   & Parameters                \\
 \midrule
 Cycamore & Enrichment & Tail Assay                \\
          & Separation & Separation efficiency     \\
          & Storage    & Residence Time            \\
 \midrule
 CyCLASS  & Reactor    & Cycle Length              \\
          &            & Power                     \\
          &            & Fuel Enrichment (PWR-UOX) \\

 \bottomrule
 \end{tabular}

   \label{tab:package_uncertainty}
 \end{table}

\section{The Experiment}
